Embodied Neuromorphic Benchmarks

### 2015-08-08 paper/paper.tex
bibliography

@@

\bibliographystyle{frontiersinSCNS_ENG_HUMS} % for Science, Engineering and Humanities and Social Sciences articles, for Humanities and Social Sciences articles please include page numbers in the in-text citations
%\bibliographystyle{frontiersinHLTH&FPHY} % for Health and Physics articles
\bibliography{test}

>>>>

The above considerations seem to indicate that even though using real-world
phyiscal hardware for benchmarking is problematic, it is still better than
using simplistic simulations which may not generalize to real tasks.  However,
we believe there is an alternate approach known as \emph{Minimal Simulation}
\cite{Jakobi97evolutionaryrobotics}.

@@

\bibliographystyle{frontiersinSCNS_ENG_HUMS} % for Science, Engineering and Humanities and Social Sciences articles, for Humanities and Social Sciences articles please include page numbers in the in-text citations
%\bibliographystyle{frontiersinHLTH&FPHY} % for Health and Physics articles
\bibliography{paper}
